Tree-structured neural networks revisited

### 2016-02-27 writing/hard_stack_paper/paper.tex
Even more affiliations.

@@

\author{
Samuel R.\ Bowman$^{\ast\dag}$ \\
\texttt{sbowman@stanford.edu} \\
\And
Jon Gauthier$^{\dag\ddag}$ \\
\texttt{jgauthie@stanford.edu} \\
\And
Abhinav Rastogi$^{\dag\S}$ \\
\texttt{arastogi@stanford.edu} \\
\AND
Raghav Gupta$^{\dag\mathparagraph}$ \\
\texttt{rgupta93@stanford.edu} \\
\And
Christopher D.\ Manning$^{\ast\dag\mathparagraph}$\\
\texttt{manning@stanford.edu}\\
\And
Christopher Potts$^{\ast}$\\
\texttt{cgpotts@stanford.edu}
\AND\\[-3ex]
{$^{\ast}$Stanford Linguistics\quad
$^{\dag}$Stanford NLP Group\quad
$^{\ddag}$Stanford Symbolic Systems}\\
{$^{\S}$Stanford Electrical Engineering\quad
$^{\mathparagraph}$Stanford Computer Science}
}

@@

\newcommand\todo[1]{\textcolor{red}{\textbf{TODO:} #1}}
\newcommand\note[1]{\textcolor{blue}{\textbf{NOTE:} #1}}

\begin{document}
\maketitle
\todo{Anonymize.}

\begin{abstract}
\begin{itemize}
\item TreeRNNs are great, don't work for big data.
\item We present the transition-based TreeRNN implementation -- makes efficient training possible, show that it helps relative to seq models.
\item Further, attention has proven powerful for extending sequence models. We introduce constit-by-constit attention, and find it to be effective here, too.
\end{itemize}
\end{abstract}

>>>>

\newcommand\todo[1]{\textcolor{blue}{\textbf{TODO:} #1}}
\newcommand\result[1]{\textcolor{red}{\textbf{RESULT NEEDED:} #1}}
\newcommand\question[1]{\textcolor{orange}{\textbf{OPEN QUESTION:} #1}}

@@

\author{
Samuel R.\ Bowman$^{\ast\dag}$ \\
\texttt{sbowman@stanford.edu} \\
\And
Jon Gauthier$^{\dag\ddag}$ \\
\texttt{jgauthie@stanford.edu} \\
\And
Abhinav Rastogi$^{\S\mathparagraph}$ \\
\texttt{arastogi@stanford.edu} \\
\AND
Raghav Gupta$^{\parallel}$ \\
\texttt{rgupta93@stanford.edu} \\
\And
Christopher D.\ Manning$^{\ast\dag\parallel}$\\
\texttt{manning@stanford.edu}\\
\And
Christopher Potts$^{\ast}$\\
\texttt{cgpotts@stanford.edu}
\AND\\[-3ex]
{$^{\ast}$Stanford Linguistics\quad
$^{\dag}$Stanford NLP Group\quad
$^{\ddag}$Stanford Symbolic Systems}\\
{$^{\S}$Stanford Electrical Engineering\quad
$^{\mathparagraph}$Stanford AI Lab\quad
$^{\parallel}$Stanford Computer Science}
}

@@

\begin{document}
\maketitle
\begin{abstract}
\begin{itemize}
\item TreeRNNs are great, don't work for big data.
\item We present the transition-based TreeRNN implementation -- makes efficient training possible, show that it helps relative to seq models.
\item Further, attention has proven powerful for extending sequence models. We introduce constit-by-constit attention, and find it to be effective here, too.
\end{itemize}
\end{abstract}

\todo{Anonymize.}
